FocalGstar

### 2017-06-15 analysis.Rmd
updated legends for confidence intervals

lines(y1, col = "blue", lw = 2)
lines(y2, col = "red", lw = 2)
legend(1,1, c("G*", "Focal G*"), fill = c("blue", "red"))
mtext("CI: FMsize and WMsize", line = -1, adj = .98)
```

@@

plot(NA,
     ylab = expression(SoH^Up),
     xlab = sprintf("Weight matrix size"),
     xlim = c(7,43), ylim = c(0,1))
plotCI(x = mean$Group.1,
       y = mean$x,
       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
plotCI(x = meanG$Group.1,
       y = meanG$x,
       uiw = sdG$x, err = "y", pch = 20, slty = 3, scol = "blue", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
lines(meanG$Group.1, meanG$x, col = "blue", lw = 4)
legend("topleft", c("Focal G*", "G*") , fill = c("red", "blue"))

@@

plot(NA,
     ylab = expression(SoH^Down),
     xlab = sprintf("Weight matrix size"),
     xlim = c(7,43), ylim = c(0,1))
plotCI(x = mean$Group.1,
       y = mean$x,
       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
plotCI(x = meanG$Group.1,
       y = meanG$x,
       uiw = sdG$x, err = "y", pch = 20, slty = 3, scol = "blue", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
lines(meanG$Group.1, meanG$x, col = "blue", lw = 4)
legend("topleft", c("Focal G*", "G*") , fill = c("red", "blue"))

@@

mean <- aggregate(d3$Up, by = list(d3$Z + 1), mean)
sd <- aggregate(d3$Up, by = list(d3$Z + 1), sd)
meanG <- aggregate(d3global$Up, by = list(d3global$Z + 1), mean)
sdG <- aggregate(d3global$Up, by = list(d3global$Z + 1), sd)
plot(NA,
     ylab = expression(SoH^Up),
     xlab = sprintf("Aggregation levels"),
     xlim = c(2,6), ylim = c(0,1))
plotCI(x = mean$Group.1,
       y = mean$x,
       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
plotCI(x = meanG$Group.1,
       y = meanG$x,
       uiw = sdG$x, err = "y", pch = 20, slty = 3, scol = "blue", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
lines(meanG$Group.1, meanG$x, col = "blue", lw = 4)
legend("topleft", c("Focal G*","G*") , fill = c("red","blue"))

mean <- aggregate(d3$Down, by = list(d3$Z + 1), mean)
sd <- aggregate(d3$Down, by = list(d3$Z + 1), sd)
meanG <- aggregate(d3global$Down, by = list(d3global$Z + 1), mean)
sdG <- aggregate(d3global$Down, by = list(d3global$Z + 1), sd)
plot(NA, 
     ylab = expression(SoH^Down),
     xlab = sprintf("Aggregation levels"),
     xlim = c(2,6), ylim = c(0,1))
plotCI(x = mean$Group.1,
       y = mean$x,
       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
plotCI(x = meanG$Group.1,
       y = meanG$x,
       uiw = sdG$x, err = "y", pch = 20, slty = 3, scol = "blue", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
lines(meanG$Group.1, meanG$x, col = "blue", lw = 4)
legend("topleft", c("Focal G*","G*") , fill = c("red","blue"))
```

@@

mean <- aggregate(d3$Up, by = list(d3$F + 12), mean)
sd <- aggregate(d3$Up, by = list(d3$F + 12), sd)
plot(NA,
     ylab = expression(SoH^Up),
     xlab = "Focal matrix size",
     xlim = c(29, 137), ylim = c(0, 1))
plotCI(x = mean$Group.1, y = mean$x, uiw = sd$x, err = "y", pch = 20, slty = 3,
       scol = "red", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
legend("topleft", c("Focal G*") , fill = c("red"))

mean <- aggregate(d3$Down, by = list(d3$F + 12), mean)
sd <- aggregate(d3$Down, by = list(d3$F + 12), sd)
plot(NA,
     ylab = expression(SoH^Down),
     xlab = "Focal matrix size",
     xlim = c(29,137), ylim = c(0,1))
plotCI(x = mean$Group.1,
       y = mean$x,
       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
legend("topleft", c("Focal G*") , fill = c("red"))

>>>>

lines(y1, col = "blue", lw = 2)
lines(y2, col = "red", lw = 2)
legend(1,1, c("G*", "Focal G*"), fill = c("blue", "red"))
```

@@

plot(NA,
     ylab = expression(SoH^Up),
     xlab = sprintf("Weight matrix size"),
     xlim = c(7,43), ylim = c(0,1))
plotCI(x = mean$Group.1,
       y = mean$x,
       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
plotCI(x = meanG$Group.1,
       y = meanG$x,
       uiw = sdG$x, err = "y", pch = 20, slty = 3, scol = "blue", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
lines(meanG$Group.1, meanG$x, col = "blue", lw = 4)
legend("topleft", c("Focal G*", "G*") , fill = c("red", "blue"))
mtext("CI: FMsize + Aggregation", line = -1, adj = .98)

@@

plot(NA,
     ylab = expression(SoH^Down),
     xlab = sprintf("Weight matrix size"),
     xlim = c(7,43), ylim = c(0,1))
plotCI(x = mean$Group.1,
       y = mean$x,
       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
plotCI(x = meanG$Group.1,
       y = meanG$x,
       uiw = sdG$x, err = "y", pch = 20, slty = 3, scol = "blue", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
lines(meanG$Group.1, meanG$x, col = "blue", lw = 4)
legend("topleft", c("Focal G*", "G*") , fill = c("red", "blue"))
mtext("CI: FMsize + Aggregation", line = -1, adj = .98)
```

@@

mean <- aggregate(d3$Up, by = list(d3$Z + 1), mean)
sd <- aggregate(d3$Up, by = list(d3$Z + 1), sd)
meanG <- aggregate(d3global$Up, by = list(d3global$Z + 1), mean)
sdG <- aggregate(d3global$Up, by = list(d3global$Z + 1), sd)
plot(NA,
     ylab = expression(SoH^Up),
     xlab = sprintf("Aggregation levels"),
     xlim = c(2,6), ylim = c(0,1))
plotCI(x = mean$Group.1,
       y = mean$x,
       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
plotCI(x = meanG$Group.1,
       y = meanG$x,
       uiw = sdG$x, err = "y", pch = 20, slty = 3, scol = "blue", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
lines(meanG$Group.1, meanG$x, col = "blue", lw = 4)
legend("topleft", c("Focal G*","G*") , fill = c("red","blue"))
mtext("CI: ??? TODO ???", line = -1, adj = .98)

mean <- aggregate(d3$Down, by = list(d3$Z + 1), mean)
sd <- aggregate(d3$Down, by = list(d3$Z + 1), sd)
meanG <- aggregate(d3global$Down, by = list(d3global$Z + 1), mean)
sdG <- aggregate(d3global$Down, by = list(d3global$Z + 1), sd)
plot(NA, 
     ylab = expression(SoH^Down),
     xlab = sprintf("Aggregation levels"),
     xlim = c(2,6), ylim = c(0,1))
plotCI(x = mean$Group.1,
       y = mean$x,
       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
plotCI(x = meanG$Group.1,
       y = meanG$x,
       uiw = sdG$x, err = "y", pch = 20, slty = 3, scol = "blue", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
lines(meanG$Group.1, meanG$x, col = "blue", lw = 4)
legend("topleft", c("Focal G*","G*") , fill = c("red","blue"))
mtext("CI: ??? TODO ???", line = -1, adj = .98)
```

@@

mean <- aggregate(d3$Up, by = list(d3$F + 12), mean)
sd <- aggregate(d3$Up, by = list(d3$F + 12), sd)
plot(NA,
     ylab = expression(SoH^Up),
     xlab = "Focal matrix size",
     xlim = c(29, 137), ylim = c(0, 1))
plotCI(x = mean$Group.1, y = mean$x, uiw = sd$x, err = "y", pch = 20, slty = 3,
       scol = "red", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
legend("topleft", c("Focal G*") , fill = c("red"))
mtext("CI: ??? TODO ???", line = -1, adj = .98)

mean <- aggregate(d3$Down, by = list(d3$F + 12), mean)
sd <- aggregate(d3$Down, by = list(d3$F + 12), sd)
plot(NA,
     ylab = expression(SoH^Down),
     xlab = "Focal matrix size",
     xlim = c(29,137), ylim = c(0,1))
plotCI(x = mean$Group.1,
       y = mean$x,
       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
legend("topleft", c("Focal G*") , fill = c("red"))
mtext("CI: ??? TODO ???", line = -1, adj = .98)
```
